\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}   % For mathematical formulas
\usepackage{graphicx}  % For including graphics
\usepackage{cite}      % For bibliography management
\usepackage{hyperref}  % For hyperlinks

\title{Title of the Research Paper}
\author{\IEEEauthorblockN{Your Name}
\IEEEauthorblockA{Your Institution\\
Your Email}
}

\begin{document}

\maketitle

\begin{abstract}
    This is a brief summary of the research paper, providing an overview of the main objectives, methodology, results, and conclusions. The abstract should be concise, usually around 150-250 words.
\end{abstract}

\begin{IEEEkeywords}
    Keyword1, Keyword2, Keyword3, Keyword4
\end{IEEEkeywords}

\section{Introduction}
The introduction provides background information on the topic of the research, outlines the problem being addressed, and states the objectives of the study. It may also include a brief literature review.

\section{Methodology}
In this section, describe the methods used in your research. Include information about the experimental design, materials, procedures, and any statistical analyses performed.

\section{Results}
Present the findings of your research. Use tables, figures, and graphs where necessary to illustrate your results. Each table or figure should be accompanied by a caption explaining its contents.

\subsection{Subsection Title}
If needed, you can include subsections to further organize your results.

\section{Discussion}
Interpret the results in this section. Discuss their implications, limitations, and how they relate to previous research. Consider addressing any unexpected findings.

\section{Conclusion}
Summarize the main findings and contributions of your research. You may also suggest directions for future research.

\section*{Acknowledgments}
Acknowledge any individuals or organizations that contributed to your research but do not meet the criteria for authorship.

\bibliographystyle{IEEEtran}  % IEEE bibliography style
\bibliography{references}       % Include your bibliography file (references.bib)

\end{document}
